The \dealii{} Library, Version 9.0

### 2018-04-11 9.0/paper.tex
Minor edits.

\item
  \dealii{} first offered support for C++11 features in version 6.2, which was
  published in 2009: This release is the first to \emph{require} a compiler
  supporting C++11. \dealii{} now uses language improvements such as using
  \texttt{emplace\_back()} instead of \texttt{push\_back()}, moving objects
  instead of copying them, using \texttt{nullptr} instead of \texttt{NULL}, and
  marking unimplemented constructors with \texttt{=delete;} instead of making
  them \texttt{private}. These changes include some minor incompatibilities: all
  \texttt{clone} functions (such as \texttt{FiniteElement::clone} and
  \texttt{Mapping::clone}) now return \texttt{std::unique\_ptr}s instead of
  C-style raw pointers. Indeed, nearly every interface that returns a pointer
  now returns either a \texttt{std::shared\_ptr} or \texttt{std::unique\_ptr},
  which clarifies object ownership responsibilities and avoids memory leaks.

>>>>

\item
  \dealii{} first offered support for a subset of C++11 features in
  version 6.2, released in 2009. The current release is the first to \emph{require} a compiler
  supporting C++11. \dealii{} now uses language improvements such as using
  \texttt{emplace\_back()} instead of \texttt{push\_back()}, moving objects
  instead of copying them, using \texttt{nullptr} instead of \texttt{NULL}, and
  marking members with \texttt{=delete;} and \texttt{=default;} where
  appropriate. These changes include some minor incompatibilities: all
  \texttt{clone()} functions (such as \texttt{FiniteElement::clone()} and
  \texttt{Mapping::clone()}) now return \texttt{std::unique\_ptr}s instead of
  C-style raw pointers. Indeed, nearly every interface that returns a pointer
  now returns either a \texttt{std::shared\_ptr} or \texttt{std::unique\_ptr},
  which clarifies object ownership responsibilities and avoids memory leaks.
